---
title: "Tidyverse_titanic"
author: "Scott G Daniel, PennCHOP Microbiome Center"
date: "3/12/2019"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(tidyverse)
```

# Titanic dataset

## Starting

```{r loading}


passengers <- read.csv("train.csv")

```

### Summarize titanic using a pipe

```{r}
passengers %>%
  summary()


```
### Summarize titanic after dropping na

```{r}

passengers %>%
  drop_na() %>%
  summary()
```

## Filter

### Males

```{r}
passengers %>%
  filter(Sex == "male") %>%
  drop_na() %>%
  head()
```
### Females

```{r}
passengers %>%
  filter(Sex == "female") %>%
  drop_na() %>%
  head()
```
## Arrange

### By fare (ascending)
```{r}
passengers %>%
  arrange(Fare)%>%
  drop_na() %>%
  head()
```

### By fare (descending)
```{r}
passengers %>%
  arrange(desc(Fare))%>%
  drop_na() %>%
  head()
```

## Mutate

### Create new column FamSize (size of family)

```{r}
passengers %>%
  mutate(FamSize = Parch + SibSp)%>%
  drop_na() %>%
  arrange(desc(FamSize)) %>%
  head()
```

### Turn numerical values of Survived column to "No" & "Yes" (new data frame)

```{r}
passengers1 <- passengers %>%
  mutate(Survived = if_else(Survived == 0, "No", "Yes")) 

head(passengers1)
```

## Goodness-Gracious-Plotting

### Plot barplot of passenger Sex

```{r}
ggplot(passengers, aes(x = Sex)) +
  geom_bar()
```

### Scatter plot of Age vs Fare and colored by Sex

```{r}
ggplot(passengers, aes(x = Age, y = Fare, color = Sex)) +
  geom_point()
```

### Scatter plot of Age vs Fare colored by Sex faceted by Survived

```{r}
passengers1 %>%
  drop_na() %>%
ggplot(aes(x = Age, y = Fare, color = Sex)) +
  geom_point() +
  facet_grid(~Survived)
```


